\documentclass[11pt,letterpaper]{report}

\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[english]{isodate}
\usepackage[parfill]{parskip}
\usepackage{graphicx}
\usepackage{subfigure}
%\usepackage[hidelinks]{hyperref}
\usepackage{hyperref}

\usepackage{sstmanual}

\addtolength{\oddsidemargin}{-.75in}
\addtolength{\evensidemargin}{-.75in}
\addtolength{\textwidth}{1.5in}

\addtolength{\topmargin}{-.75in}
\addtolength{\textheight}{1.5in}

\setcounter{secnumdepth}{2}
\setcounter{tocdepth}{4} % show paragraphs in TOC

\title{SST Core Python Module Manual}
\date{\today}

\begin{document}
\maketitle
\newpage

\pagenumbering{Roman}

\begingroup
  \hypersetup{hidelinks}
  \tableofcontents
\endgroup
\newpage
%\listoffigures
%\newpage
%\listoftables
%\newpage
\pagenumbering{arabic}

\chapter{Introduction}

SST provides a python module to allow interaction with the simulation
build system.  This python module is used in the input python script
for the purpose of building the graph that represents the simulation
to be performed.  This is done by providing class and functions to
define the elements of the simulation, their parameters, and how they
are interconnected.  The user can also optionally enable statistics
and create a user specified partitioning for the described model.
Behind the scenes, these classes will build the c++ data structure
that is used by SST to construct the simulation model.

The SST core python module is defined in cpython and is only
available in the python interpreter launched within a running SST
executable.  The module is accessed by importing the sst module.  This
can be done in a number of ways.  The two most common being:

\begin{pycodeexample}{}
# Import SST python module using sst. prefix
import sst
# Import SST python module members into current namespace
from sst import *
\end{pycodeexample}

Within this module, there are a number of available classes and global
functions.  The available classes are: Component, SubComponent, Link,
StatisticOutput and StatisticGroup.  The global functions are divided
between general functions and functions operating on or returning one
of the available objects.  This document will first discuss the
available classes in the SST python module and will then document the
global functions.


\input{classes.tex}

\input{globals.tex}
\end{document}
