\section{StatisticOutput}

The StatisticOutput object is used to configure the output type and
options for statistics and is for use with StatisticGroup.  For the
global statistics output, see the global functions:
\lstinline{setStatisticOutput()}. \lstinline{setStatisticOutputOption()}
and \lstinline{setStatisticOutputOptions()}.

The StatisticOutput object is created using:

\begin{functiondoc}{StatisticOutput(type, params=None)}
  { Constructor for StatisticOutput }

  \param{type} (type: string) type of Statistic output to use

  \param{params} (type:dict) Diction of key value pairs to be added to
  the StatisticOutput's parameters

  \returns{created StatisticOutput object}
\end{functiondoc}

\begin{functiondoc}{addParam(key, value)}
  { Adds a parameter to the Params object for the StatisticOutput.}

  \param{key} (type: string) name of the parameter

  \param{value} (type: varies) value of the parameter.  This can be
  almost any python object and the \lstinline{__str__} method will be
  called to get a string representation.  A list can be passed to this
  call when the find\_array function is used in the class to retrieve
  the parameters.

\noreturn
\end{functiondoc}

\begin{functiondoc}{addParams(params)}
  { Adds multiple parameters to the Params object for the StatisticOutput.}

  \param{params} (type: dict) a python dict of key, value pairs.
  \lstinline{See addParam()} description for information about how key
  and value are used.

\noreturn
\end{functiondoc}





